%SUbmission Instruction
\begin{center}
    \Huge{Submission Instruction}
\end{center}
\bigskip

\large{
The last date to submit this assignment is \submissionDeadline. No late submissions will be allowed. All the answers must be handwritten and scanned and sent as PDF files. No other file formats will be allowed.\\
If you have any health condition refraining you from submitting on time, you have to inform me before \noticeDeadline for prior approval for late submission. It will to my discretion to allow you for late submission based on the severity of your condition.\\
You should only submit the questions from set you are assigned. Submission of any other set as well as copying from other students answers will be heavily penalized.\\
Use the attached format for front Page. The front page can be printed or handwritten.\\
The procedure to submit assignments is as follows:
\begin{itemize}
    \item Prepare your assignment by scanning the handwritten assignments and converting them to PDF. The pages should be in order. No effort will be made to check disordered files or late submissions. All the pages should be in a single PDF file.
    \item Rename your file as \textbf{\fileName}, where the last 12 digits are your registration number. Any other format of naming will not be allowed and will not be considered for grading.
    \item Send your assignment to the following address \href{mailto:\emailAddress?subject=\emailSubject }{\emailAddress} . There is no need to CC or send any copy to my other email address.
    \begin{itemize}
        \item The subject line of your email should read as \textbf{\emailSubject} . Where the last 12 digits are your registration number. Any other format will eliminate the chance of your email to reach the correct folder of my email. You are suggested to copy the text if necessary.
    \end{itemize}
\end{itemize}

}
